\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-11-27 src/chain.tex
cactus

\paragraph*{Model.}
%
An instance of the \scplong (\scp) problem is composed of three
components, a physical network, a virtual specification, and placement
costs:
\begin{description}
\item[Physical network:]
%
  The physical network is a graph $G = (V,E)$.  Each node $v \in V$
  has a non-negative processing capacity $p(v)$, and each directed
  edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
%
  Without loss of generality, we assume that $p(s) = p(t) = 0$.

@@

\paragraph*{Notation.}
%
Given a virtual DAG $\calG$, we assume the existence of a topological
sorting of the vertices and write $\alpha \prec \beta$ if $\alpha$
precedes $\beta$ in this ordering.  If the physical network is a DAG,
then we make a similar assumption and write $v \prec u$ if $v$
precedes $u$ in this ordering.

@@

>>>>

\subsection*{Model.}
%
An instance of the \scplong (\scp) problem is composed of three
components, a physical network, a virtual specification, and placement
costs:
\begin{description}
\item[Physical network:]
%
  The physical network is a graph $G = (V,E)$.  Each node $v \in V$
  has a non-negative processing capacity $p(v)$, and each directed
  edge $e \in E$ has a non-negative bandwidth capacity $b(e)$.
%
  Without loss of generality, we assume that $p(s) = p(t) = 0$.

@@

\subsection*{Notation.}
%
Given a virtual DAG $\calG$, we assume the existence of a topological
sorting of the vertices and write $\alpha \prec \beta$ if $\alpha$
precedes $\beta$ in this ordering.  If the physical network is a DAG,
then we make a similar assumption and write $v \prec u$ if $v$
precedes $u$ in this ordering.

@@

\subsection*{Discussion About the Orientation Phase}
We now discuss the orientation phase and propose a different method to apply 
an orientation to an undirected graph.
While the proposed method does not surpass the trivial orientation in the worse case, 
in certain cases, the new method yields an exponential improvement over the trivial one.

The orientation works as follow:
given an undirected graph $G = (V, E)$ we first find its block tree 
(where every vertex in the tree is a maximal subgraph of $G$ without a cut-vertex),
then, on the unique  path from $s$ to $t$ we internally orient each block arbitrarily to
produce a DAG.
Note that if $B_1, \ldots, B_k$ are the blocks of $G$ on the path from $s$ to $t$ then
the first and last vertices w.r.t to each block are known and only the order
of the internal neighborly vertices in each block is needed to be determined,
thus, we can find all relevant orientations by repeating the process above
$\Pi_{i = 1}^k n(B_i)$ times, where $n(B_i)$ is the number of internal neighborly vertices
in $B_i$.

\begin{theorem}
There is an FPT algorithm that finds a $(1+\eps)$-approximate placement after
$\Pi_{i = 1}^k n(B_i)$ iterations.
\end{theorem}

Figure~\ref{fig:or2} shows that in some cases this approach is faster than the trivial one.
We also note that if the given graph is a cactus graph then using this approach result in 
a polynomial algorithm.
This special case of cactus graph was already considered in \cite{Stefan} and was also found
as a special case for which a hard problem becomes tractable.

\begin{theorem}
There is a polynomial algorithm that finds a $(1+\eps)$-approximate placement 
for cactus graph.
\end{theorem}

\begin{figure}
\begin{center}
\input{fig-or2}
\end{center}
\caption{
A undirected graph with its block marked in a dashed, green lines.
In this instance, using the trivial approach the orientation phase takes 16! iterations,
while using the second approach we only need 3! iterations.
\label{fig:or2}
}
\end{figure}   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
